---
title: "Week 12 Activity"
author: "Tanuj Gaikwad"
date: "April 8, 2022"
output: html_notebook
---

### Load Packages
```{r warning = FALSE, message = FALSE}
#Load Packages
library(rvest)
library(tidyverse)
```

### Read in Data
```{r warning = FALSE, message = FALSE}
#Read in Data
data <- read.delim("Data_RegEx2.txt", fileEncoding = "UTF-8", header = F, quote = "")

head(data)
```

### First Cleaning of Data
```{r warning = FALSE, message = FALSE}
NewTable <- 
  as.data.frame(matrix(data$V1, ncol = 16, byrow = T)) %>%
  rename("Position" = "V1", "Player" = "V2", "FinalScore" = "V3", "THRU" = "V4", "TODAY" = "V5",
         "SGPutt" = "V6", "SCARG" = "V7", "SGAPP" = "V8", "SGOTT" = "V9", "SGT2G" = "V10", "SGTOT" = "V11",
         "DrDist" = "V12", "DrAcc" = "V13", "GIR" = "V14", "FairProx" = "V15", "Scrambling" = "V16") %>% #Rename Col Names
  extract(col = Player, into = c("Last", "First") , regex = "([\\w\\s]+)(\\s\\w.+)") %>% #Separate Last & First Names of Players
  unite("Player", c("First", "Last"), sep = " ") %>% #Unite them again in "First Last" order
  filter(Position != "WD") %>% #Filter out withdrawn players
  mutate(THRU = replace(THRU, THRU == "—", NA)) %>% #Make all hyphens into NA values
  mutate(TODAY = replace(TODAY, TODAY == "—", NA)) #Make all hyphens into NA values

#View Head & Tail of table for final checks before graphing
head(NewTable)

tail(NewTable)
```


### Second Cleaning of Data
```{r warning = FALSE, message = FALSE}
#Change formatting for variables that need to be charted
NewTable$SGTOT = as.numeric(NewTable$SGTOT)
NewTable$GIR = as.numeric(gsub("[\\%]", "", NewTable$GIR))

#Make new column based on if Cut or Not
NewTable <- 
  mutate(NewTable, Cut = ifelse(Position == "CUT", "Missed Cut", "Made Cut"))
```

### Boxplot 1: Shots Gained Total
```{r warning = FALSE, message = FALSE}
#First Plot
ggplot(NewTable, aes(x = Cut, y = SGTOT)) + 
  geom_boxplot(aes(color = Cut)) +
  labs(title = "Boxplot Shots Gained Total",
       y = "Shots Gained Total",
       x  = "CUT")
```
This graph gives a good representation of the overall average range of a player's score compared to the average pool of scores from all players. Those with a more positive score end up as "Made Cut" and those who lack are in the "Missed Cut" category. 

### Boxplot 2: Greens in Regulation
```{r warning = FALSE, message = FALSE}
ggplot(NewTable, aes(x = Cut, y = GIR)) + 
  geom_boxplot(aes(color = Cut)) +
  labs(title = "Boxplot Greens Hit in Regulation",
       y = "Greens in Regulation",
       x  = "CUT")
```
This graph is a representation of the amount of times players have hit the golf ball into the green. Those that "made cut" were more successful that those who "missed cut" in getting their balls on the green.